Cluster Paper

### 2015-03-31 ms.tex
added editorial
made a bunch of notes to myself.

\section{AARDVARK SIMULATION}

\section{THE HETDEX SURVEY}

@@

\subsection{Mock Observations}

@@

>>>>

\section{AARDVARK SIMULATION}
\editorial{Waiting to get a look at what Casey comes up with for the proposal we are supposedly writing. If he does a decent job then I'll try to expand it a bit and fill out this section.}

\section{THE HETDEX SURVEY}
\editorial{This should probably go into the introduction. I don't think we need a whole section on something that a bunch of papers have already talked about.}

@@

\subsection{Mock Observations}
\editorial{Here we need to talk about about how we set up the observations to look like what we think the HETDEX survey will see. It should be more techincal than the general discussion about what the survey hopes to accomplish, that'll go in the intro. A zoomed figure showing the tiling footprints would be appropriate.}

@@

\editorial{Need to talk about how the parameters are some what up for debate, and vary from study to study. I think we should just use the params from Evrard2008 and call it a day. We can show a figure where we fit the data for the parameters, but that seems kinda silly to calibrate the data on the the data we are trying to fit.}
